Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-02 paper.qmd
Added all the langevitour which produce the projections

projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558,-0.23854,-0.63659,0.35753))

@@

projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558, -0.23854, -0.63659, 0.35753))

@@

## First projection
projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558,-0.23854,-0.63659,0.35753))

@@

@@

>>>>

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < benchmark_gau1)
```

```{r}
#| label: langevitour-five-gau-tsne-proj
#| eval: false

df_model_data_n <- bind_rows(data_gau, df_b)

langevitour::langevitour(df_model_data_n[1:(length(df_model_data_n)-1)],
                         lineFrom = distance_df_small_edges$from,
                         lineTo = distance_df_small_edges$to,
                         group = factor(df_model_data_n$type,
                                        c("data", "model")),
                         levelColors = c(clr_choice, "#000000"))
```

```{r}
#| label: five-gau-tsne-projs
projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558,-0.23854,-0.63659,0.35753))

@@

scaled_gau_data_model <- scaled_gau |>
  filter(type == "model") |>
  select(-type)
```

```{r}
#| label: langevitour-five-gau-umap-proj
#| eval: false

df_model_data_n <- bind_rows(data_gau, df_b)

langevitour::langevitour(df_model_data_n[1:(length(df_model_data_n)-1)],
                         lineFrom = distance_df_small_edges$from,
                         lineTo = distance_df_small_edges$to,
                         group = factor(df_model_data_n$type,
                                        c("data", "model")),
                         levelColors = c(clr_choice, "#000000"))
```

```{r}
#| label: five-gau-umap-projs
projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558, -0.23854, -0.63659, 0.35753))

@@

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < benchmark_gau1)
```

```{r}
#| label: langevitour-five-gau-pacmap-proj
#| eval: false

df_model_data_n <- bind_rows(data_gau, df_b)

langevitour::langevitour(df_model_data_n[1:(length(df_model_data_n)-1)],
                         lineFrom = distance_df_small_edges$from,
                         lineTo = distance_df_small_edges$to,
                         group = factor(df_model_data_n$type,
                                        c("data", "model")),
                         levelColors = c(clr_choice, "#000000"))
```

```{r}
#| label: five-gau-pacmap-projs
## First projection
projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558,-0.23854,-0.63659,0.35753))

@@

```{r}
#| label: langevitour-c-shaped-tsne-proj
#| eval: false

@@

```{r}
#| label: langevitour-best-fit-mnist-proj-tsne
#| eval: false
